Sentence-Matching in the Bluegrass Corpus: Methodological Considerations

### 2019-09-28 article.Rmd
delete three repeated sentences

## rearrange for easier viewing
sentences <-
  sentences %>% 
  arrange(pair_id)
```

@@

@@

Our task is find a set of eight rows and a set of eight columns and a matching between them so as to make the sum of the corresponding eight cells as small as possible.

@@

## Utility function.  Given a pair of speakers, find the best
## matching of sentences.  Uses brute force to go through
## all possible pairs of subsets of cardinality "select" from speaker A,
## with each A-set using the Hungarian Algorithm
## to find the best matching set of sentences from Speaker B.
## Keeps track of the best matching.
## Returns a data frame of results.
get_best <- function(pair, size, select, trim) {

@@

@@

## This is the function you'll actually use.
##
## data  = the original data frame
## size = number of sentences eer speaker
## select = desired number of sentence-pairs
##
## trim permites researchers to omit very high or low
## ratings from the analysis.  (Example:  setting trim = 0.1 would
## eliminate the highest and the lowest of the ten differences in ratings.)
##
## Setting trace to TRUE results in a progress report to the console
## (not needed for the current small study)
##
## Result is a list of data frames, one for each speaker-pair,
## saying which sentence goes to which, and reporting the P-values
## of the Yuen T-Test.  This allows the user to flag pairs where the
## ratings are "too different".
##
match_sentences <- function(data, size, select, trim = 0, trace = FALSE) {
  pair_ids <- sort(unique(data$pair_id))
  pairs <- length(unique(data$pair_id))
  lst <- vector(mode = "list", length = pairs)
  for (i in 1:pairs) {
    if (trace) {
      cat("Working on speaker pair with id", pair_ids[i], "...\n")
    }
    pair <- data %>% 
      filter(pair_id == pair_ids[i])
    results <-  get_best(pair, size, select, trim)
    lst[[i]] <- results
  }
  names(lst) <- pair_ids
  lst
}
```

@@

```{r cache = TRUE}
system.time(
  results <- match_sentences(
    data = sentences,
    size = 12,
    select = 8,
    trim = 0,  ## the default, actually,
    trace = FALSE
  )
)
```

@@

Here is density plot of all 9600 individual difficulty-ratings:

```{r echo = FALSE, fig.cap = "Density plot of all 9600 difficulty-ratings recorded in the study."}
s2 %>% 
  ggplot(aes(x = rating)) +
  geom_density(fill = "burlywood")
```

Next we see a violin plot of mean difficulty-ratings.  Each dot is a single sentence; its vertical height is the mean of the ratings for the ten participants who rated it.  We have separated the sentences into the 320 that were not selected as members of an optimal matching and the 640 setences that were selected.

@@

The following boxplot compare the mean difficulty-ratings of senteces spoken by foreign anf native speakers, including those sentences that were not selected as members of an optimal pairing:

>>>>

## rearrange for easier viewing
sentences <-
  sentences %>% 
  arrange(pair_id)

## Duplicate suentences, discovered by Bailey McGuffey:
## Eliminate the repeated sentences 14F4, 33N3, and 45N7 
## from the dataset:

bad_ids <- c("14AE3", "33BE5", "45BD11")
sentences <-
  sentences %>% 
  filter(!(sentence_id %in% bad_ids))
```

@@

For almost every speaker-pair, we had access to twelve sentences from each speaker in the pair. (Three sentences had to be removed from the original data, resulting in three instances in which a speaker had only eleven sentences.)

@@

(As is the case for most of the speakers, the matrix is 12-by-12 since we had twelve sentences from each speaker.  However, for three speaker-pairs one of the speakers was missing a sentence and so the corresponding matrix was either 11-by-12 or 12-by-11.)

In any event, our task is find a set of eight rows and a set of eight columns and a matching between them so as to make the sum of the corresponding eight cells as small as possible.

@@

## Utility function.  Given a pair of speakers, find the best
## matching of sentences.  Uses brute force to go through
## all possible pairs of subsets of cardinality "select" from speaker A,
## with each A-set using the Hungarian Algorithm
## to find the best matching set of sentences from Speaker B.
## Keeps track of the best matching.
## Returns a data frame of results.
get_best <- function(pair, select, trim) {

@@

  ## make all possible subsets of cardinality select from
  ## the sentences for A-speker
  size <- nrow(diff_mats[[1]])
  a_subsets_numeric <- utils::combn(x = size, m = select)

@@

## This is the function you'll actually use.
## data is the original data frame
## select = desired number of sentence-pairs
##
## trim is there in case researchers desire to omit
## very high or low ratings.  (Setting trim = 0.1 would knock out
## the highest and the lowest of the ten differences in ratings.)
##
## Setting trace to TRUE results in a progress report to the console
## (not needed for the current small study)
##
## Result is a list of data frames, one for each speaker-pair,
## saying which sentence goes to which, and reporting the P-values
## of the Yuen T-Test.  This allows the user to flag pairs where the
## ratings are "too different".
match_sentences <- function(data, select, trim = 0, trace = FALSE) {
  pair_ids <- sort(unique(data$pair_id))
  pairs <- length(unique(data$pair_id))
  lst <- vector(mode = "list", length = pairs)
  for (i in 1:pairs) {
    if (trace) {
      cat("Working on speaker pair with id", pair_ids[i], "...\n")
    }
    pair <- data %>% 
      filter(pair_id == pair_ids[i])
    results <-  get_best(pair, select, trim)
    lst[[i]] <- results
  }
  names(lst) <- pair_ids
  lst
}
```

@@

```{r cache = TRUE}
system.time(
  results <- match_sentences(
    data = sentences,
    select = 8,
    trim = 0,  ## the default, actually,
    trace = FALSE
  )
)
```

@@

We worked with 957 sentences, each of which were rated by ten study-participants.  Here is density plot of all 9570 individual difficulty-ratings:

```{r echo = FALSE, fig.cap = "Density plot of all 9570 difficulty-ratings recorded in the study."}
s2 %>% 
  ggplot(aes(x = rating)) +
  geom_density(fill = "burlywood")
```

Next we see a violin plot of mean difficulty-ratings.  Each dot is a single sentence; its vertical height is the mean of the ratings for the ten participants who rated it.  We have separated the sentences into the 317 that were not selected as members of an optimal matching and the 640 setences that were selected.

@@

The following boxplots compare the mean difficulty-ratings of senteces spoken by foreign anf native speakers, including those sentences that were not selected as members of an optimal pairing:
